\documentclass[a4paper]{book}
\usepackage{setspace}
\usepackage{scrextend}

 
\begin{document}
\setcounter{page}{92}
\markboth{\ \ \ \ \ CHAPTER SEVEN \hfill}{}

\begin{addmargin}{2em}

\begin{spacing}{1.00}
\noindent {\small \textsf{address. If you are interested in participating in this study, please email me at [email address] or phone during the day at [phone number] prior to May 10th, 2003.}}

\vspace{5mm}
\noindent {\small \textsf{As an expert in the field, your participation in this study is greatly appreciated.}}
\end{spacing}

\begin{flushleft}
\begin{spacing}{2.00}
{\small \textsf{Respectfully, [e-researcher]}}

{\small \textsf{Principle Researcher}}
\end{spacing}
\end{flushleft}
\end{addmargin}

If the e-researcher does not get a response to the letter of invitation from the participant within about a two-week period, the letter should be followed-up with an email message. This email should be brief (approximately one screen of text) and should make reference to the letter that was sent with another invitation to participate. If the e-researcher does not know the participant personally, the email should be formal, beginning with \emph{{``}Dear\_\_\_\_}\emph{''}  and a closing with \emph{{``}Regards,'' } or \emph{{``}Sincerely,'' } as well as the e-researcher's designation in the signature line (i.e., Principle Researcher or Doctoral Candidate).


Once the prospective participant has agreed to participate, a friendly and somewhat informal message should be sent describing: the purpose of the study, the process used to maintain confidentiality, how the data will be secured, when and how the results of the study will be disseminated, and other administrative and ethical information related to the study.


\begin{flushleft}

\end{flushleft}



\begin{addmargin}{2em}
\begin{flushleft}
\vspace{5mm}
\begin{center}
\textbf{{\small \textsf{Sample Letter of Confirmation and Consent}}}
\end{center}
\end{flushleft}



\begin{flushleft}
{\small \textsf{Dear [participant]:}}
\end{flushleft}



\begin{spacing}{1.00}
\noindent {\small \textsf{Thank you for responding to my invitation to participate in this study. This email provides information about the nature of the research project and the procedures.}}

\vspace{5mm}
\noindent {\small \textsf{The study focuses on the transformation that open and flexible learning is having on higher education communities in Canada. The following three research questions are explored: (i) how does e-learning impact scholarship and research? (ii) how does e-learning impact teaching and learning? (iii) how does e-learning impact administration?}}

\vspace{5mm}
\noindent {\small \textsf{I have identified you for this study, because you are involved in implementing policies in relation to the integration of new learning technologies in higher education.}}
\end{spacing}

\vspace{5mm}
\noindent {\small \textsf{If you agree to participate, you will be requested to do the following:}}


\end{addmargin}
\end{document}
